The four postulates of quantum mechanics are three

### 2020-12-01 Articles/2019-QuantumComposition/Submissions/PhysLetters/response.tex

\begin{quote}
As I look over the four criteria the editors of PRL have
given for determining whether a paper should be published in PRL, I do
not see that any of them clearly applies to this paper. This paper
will be read with interest by physicists who have thought carefully
about the logical structure of quantum theory, but I do not think PRL
is the right place to publish it.
\end{quote}

We believe the Referee has seen these four criteria in a too
restrictive light. We please ask the Referee to take a look at the PRL
papers that are usually accepted for publication. As a typical
example, the first paper that currently appears on the PRL web site is
titled ``Stochastic Interpolation of Sparsely Sampled Time Series via
Multipoint Fractional Brownian Bridges". We have been professional
physicists for decades, and none of us has any idea of what that even
means. (We emphasize that this is the first paper on the PRL web site
today: we did not choose a particularly cryptic one!) Instead, any
physicist (or even a physics student) that has taken a quantum
mechanics course (i.e. all physicists?) will understand our title and
abstract: they have met tensor products when dealing with multiple
systems.

In addition, we also believe that the way in which we construct
Hilbert spaces from physical statements is also relevant: we cannot
claim that this is a new result, of course (although we could not find
a paper where our same formalization is presented), but this is
typically not emphasized in existing literature. In particular, we
show how the link between events in probability and observables in
Hilbert spaces goes through the projective spaces, and how the choice
of representation, the choice of gauge (phase and modulus of the state
vectors), plays into that. So, in addition to our main result, we also
claim that popularizing this particular connection is also a strength
of our paper.

\begin{quote}
I also have a couple of specific comments. 1. I think the
authors are emphasizing too strongly the smallness of the number of
postulates they are using (e.g., in the paper's title).
\end{quote}

We used the usual quantum postulates that appear in the literature,
e.g. in the referenced literature. We have no qualms in adding
postulates if the Referee suggests that we should do it. Our title is
invariant: indeed, we could also title our paper ``The five postulates
of quantum mechanics are four" or so on for any n: ``The n postulates
of quantum mechanics are n-1". Our main result is that we can remove
one of the postulates (the tensor product one): how many we start from
is not very relevant.

\begin{quote} As I was
reading the main text, it felt as if the authors were sometimes
finding new postulates in their interpretations of the words used in
definitions, and yet they were declining to call them postulates,
possibly because to do so would contradict the paper's title. I
understand that these `smaller' assumptions can be thought of as
simply making precise the meanings of commonly used expressions-- this
fact becomes clearer in the supplementary information. But strictly speaking, these are genuine assumptions.\end{quote}

We disagree: we did not add ``new postulates". 
Let us first be precise as to what a postulate is.
If one looks carefully, all postulates of quantum mechanics links something
defined within the physics world (e.g. states, observables, composite system,
time evolution) to some mathematical object (e.g. rays in a Hilbert space, Hermitian
operators, tensor product, unitary evolution). The idea is that we are
establishing a link between two different definitions (the physical
and the mathematical) that have no a priori justification. But each
element is well defined within its realm. We are not adding new postulates in the sense that we are not adding any
new link of this kind. What we are doing is showing that the definition of 
a composite system, which is ultimately a definition (NOT a postulate) within the physics
realms, together with the links already established between state space/Hilbert
space and measurment/Born rule is enough to demonstrate that the state space of the composite
system must be the tensor product of the subsystems.

More specifically, for example, there is a fundamental difference between a statement
like ``the state of a quantum system is represented by a vector in a
Hilbert space" and something like ``the state of a composite system
will fully determine the probability distribution of the observable of
all its parts and only of its parts." The first connects two
completely distinct elements, the physical preparation of a quantum
system and the mathematical construct of a Hilbert space. There is no
a priori reason for that and we are not giving one in this paper. The
second is defining an object based on the other. That is, we do not
define composite systems in some other way and than later we
independently find that they have the property of characterizing the
subsystems.  We define the composite system to be that. There is no
assumption being made: it is just a definition, and it is the natural
definition that comes from our physical intuition.

\begin{quote} For
example, Definition I.4, part 2, which says essentially that no new
orthogonal states arise when one combines two systems, is a
substantial postulate. After all, it is not the case that no new
states at all arise when one combines two systems-- entangled states
arise, and they are new. One can imagine a world in which not only
entangled states but also new orthogonal states arise. We do not live
in that world, but one needs a postulate to rule out that world. For
the authors, that postulate is Definition I.4, part 2.
\end{quote}

That "world" would simply correspond to a different definition of a composite system. Whereas we used the natural one: the (set) union of the subsystems. 
In the standard definition, the
composite system must still define all the properties of the subsystems. A new orthogonal state would not be part of the set of eigenstates of the
operators corresponding to the observables of the subsystem.

We understand that our paper was definitely unclear on this and we have
clarified this point.

Of course, entangled states arise and that is a
trivial consequence of linearity: we start from FACTORIZED states,
those are all we need to obtain tensor products, but once tensor
products are established, then ENTANGLED states arise immediately from
linearity in the composite system's Hilbert space.

\begin{quote}
(Note that the authors' informal definition of a composite
system, which is that it consists of nothing but the two systems,
could alternatively be read as excluding entangled states. Indeed, a
reader not familiar with quantum theory might well read it that way. I
mention this just to point out the ambiguity associated with an
informal definition and to highlight the importance of the actual
mathematical postulate.)
\end{quote}

We do agree that the mathematical definitions are important to precisely
address the issue: that is why we have included all the mathematical
details in the supplementary material. However, the mathematical definitions
are not as arbitrary as the referee implies.

As the Referee correctly points out, our definition certainly does not
exclude entangled states. However, we see the Referee's point and we
agree that a reader unfamiliar with quantum theory might get confused,
so we added an explicit mention that our construction can be extended
to include entangled states, which are the ones that do not satisfy
statistical independence. We added this at the end of the paragraph,
rather than at the end of that sentence, because we did not want to
ruin the flow of the narration by introducing the concept of "states"
in that sentence (which refers to systems).

\begin{quote}
2. On page 2, postulate (a) begins, 'The state of a system
is described by a ray...'. As expressed here, this postulate actually
contradicts the authors' ultimate conclusion, which allows entangled
states of the combined system. As the authors certainly know very
well, if the combined system is in an entangled state, the state of
each component system is not described by a ray in that system's
Hilbert space. I'm not sure why the authors didn't say, 'A pure state
of a system is described by a ray...'. (The word 'pure' is missing
also in the statement of this postulate in the supplementary
information.)
\end{quote}

Definitely: the word 'pure' is missing! We apologize for this
oversight and thank the Referee for pointing it out. We certainly
should have added the specification that the postulate (as expressed
in our paper) refers to pure states. Also Referee A implicitly pointed
this out. We have now corrected it.

In conclusion, we thank the Referee B for his/her insightful
observations and helpful comments. We believe that his/her assessment
on the suitability of our paper for PRL stems for an overly
restrictive interpretation of the publishing criteria, as discussed
above, and from giving more weight to the supplementary information
than to the paper. The paper mainly contains the physical ideas (which
we believe are our main contribution) whereas the supplementary
information contains only the mathematical details, as the Referee
also pointed out.

In this respect, before it was possible to attach supplementary
material to PRLs, we used to write a PRL to give the main idea and
then an adjoining PRA or PRD paper to provide the technical
details. If the Referee suggests so, we can do it also in this case
(by transforming the supplementary material into a PRA
paper). However, we would rather not do that.

--------------------

In closing, we were very pleasurably surprised by the quality of both
reports and we thank both Referees for their time they spent in
evaluating our paper.

Sincerely,

The Authors

\end{document}
